---
title: "LogisticRegression"
output: html_document
---

The library for plot and data frame
```{r setup, include=FALSE}
library(tidyverse)
library(broom)
```

Load the data from the web and assign to df
```{r}
url='https://github.com/prasertcbs/basic-dataset/raw/master/study_hours.csv'
df <- read_csv(url)
```

Plot the relation of x is hours and y is pass, %>% pass left hand to right hand
```{r}
df %>% ggplot(aes(x=Hours, y=Pass)) + geom_point()
```

Plot linear regression (for checking only)
```{r}
df %>% ggplot(aes(x=Hours, y=Pass)) + geom_point() +  stat_smooth(method="lm", se=FALSE)
```

Method is glm (Generalized linear model) Binomial is binary
```{r}
df %>% ggplot(aes(x=Hours, y=Pass)) + geom_point() + stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE) + labs(y='prop of passing exam')
```

Generalized linear model
```{r}
model <- glm(Pass ~ Hours, data = df, family = "binomial")
model
```

Summary model to check the significant difference of intercept and hours
```{r}
summary(model)
```

Check the fit value
```{r}
model$fitted.values
predict(model,type="response")
```

Cut the value more than 0.5 to True and False
```{r}
prob <- predict(model,type="response")
predict <- as.numeric(prob>.5)
predict
```
